\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-02-23 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
correct the \center L801 703(?)

%%%%%%%%%%%%%
\begin{figure}
\centering
\subfigure[map of permeabilities]{\includegraphics[width=0.5\textwidth]{./Pics1/map_of_perm_1.pdf}}\\[2mm]%
\subfigure[flow at start]{\includegraphics[width=0.5\textwidth]{./Pics1/5reg_dinlet_adapt_100.pdf}}%
\caption{In fig.(a) there is the map of permeabilities as this will be implemented in this case while in fig.(b) there is an illustration of the adaptive mesh just in the beggining of the simulation.}
\label{fig:3testcase_a}
\end{figure}

\begin{figure}
\centering
\subfigure[dual inlet flow, fixed mesh, t=500]{\includegraphics[width=0.5\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}}\\[2mm]%
\subfigure[dual inlet flow, adaptive mesh, t=500]{\includegraphics[width=0.5\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}}%
\caption{In fig.(a) there is the map of permeabilities as this will be implemented in this case while in fig.(b) there is an illustration of the adaptive mesh just in the beggining of the simulation.}
\label{fig:3testcase_b}
\end{figure

>>>>

%%%%%%%%%%%%%
\begin{figure}
\centering
\subfigure[map of permeabilities]{\includegraphics[width=0.75\textwidth]{./Pics1/map_of_perm_1.pdf}}\\[2mm]%
\subfigure[flow at start]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_adapt_100.pdf}}%
\caption{In fig.(a) there is the map of permeabilities as this will be implemented in this case while in fig.(b) there is an illustration of the adaptive mesh just in the beggining of the simulation.}
\label{fig:3testcase_a}
\end{figure}

\begin{figure}
\centering
\subfigure[dual inlet flow, fixed mesh, t=500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}}\\[2mm]%
\subfigure[dual inlet flow, adaptive mesh, t=500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}}%
\caption{In fig.(a)  fig.(b) .}
\label{fig:3testcase_b}
\end{figure}
